Efficient N-Dimensional surface estimation using Crofton formula and run-length encoding

### 2012-02-10 article/Article.tex
quelques images de plus, et un tableau de resultats

% Compute direction weights
\begin{figure}[!htb]
\begin{center}
\includegraphics[width=8cm]{images/directionsWeights2D}
\end{center}
\caption{Computation of direction weights for rectangular pixel grid. 
Black dots correspond to pixel centers. 
Angular regions are computed between direction bisectors.}
\label{fig:DirectionWeights2D3D}
\end{figure}

@@

Line densities are computed as for the planar case, by dividing distance of neighbor
voxels in direction $k$ by the volume associated to a single voxel.
When surface area is estimated by taking into account the three main direction in images, 
associated weights $c_k$ equal $1/3$. If more directions are considered, the strategy of
\cite{Ohser2000} was used: each direction was projected on the unit sphere, 
and used as a germ for computing Voronoï diagram on the unit sphere. 
The relative surface area of each spherical domain was used as weight for the
corresponding direction.

@@

% Example of reconstruction of a discrete disk
\begin{figure}[!htb]
\begin{center}
\includegraphics[width=5cm]{images/discreteDisk}
\end{center}
\caption{Discretization of a disk}
\label{fig:DiskDiscretization}
\end{figure}

@@

For each test shape, measurements were made on
several discretisation of the shape, with various orientations and various origins.

The center of each shape was chosen at random within the center pixel or voxel of the grid.

@@

\subsection{Timing evaluation}

???

@@

Figure \ref{fig:MeasureSquareOriented} shows measures obtained on discretized squares (side 30 pixels)
with various orientations. All methods oscillate around the expected value. 
Using Crofton method with only 2 directions can produce greater errors on the measure than with 4 
directions.

% Example of reconstruction of a discrete squares with various orientations
\begin{figure}[!htb]
\begin{center}
\includegraphics[width=8cm]{images/errorSquareRotated}
\includegraphics[width=8cm]{images/errorRelSquareRotated}
\end{center}
\caption{Variations of perimeter measure of a digitized square depending on the orientation}
\label{fig:MeasureSquareOriented}
\end{figure}

\section{Timing}

[c'est rapide]

>>>>

% Compute direction weights
\begin{figure}[!htb]
\begin{center}
\includegraphics[width=8cm]{images/directionWeights2D}
\includegraphics[width=7cm]{images/directionWeights3D_335}
\end{center}
\caption{Computation of direction weights for rectangular grids. 
Left: planar case. Black dots correspond to pixel centers. 
Angular regions are computed between direction bisectors.
Right: 3D case. The unit sphere is partitioned into spherical polygons
corresponding to each of the 26 oriented directions.
}
\label{fig:DirectionWeights2D3D}
\end{figure}

@@

Line densities are computed as for the planar case, by dividing distance of neighbor
voxels in direction $k$ by the volume associated to a single voxel.
When surface area is estimated by taking into account the three main direction in images, 
associated weights $c_k$ equal $1/3$. If more directions are considered, the strategy of
Ohser and M\"ucklich \cite{Ohser2000} was applied: each direction was projected on the unit sphere, 
and was used as a germ for computing Voronoï diagram on the unit sphere. 
The relative surface area of each spherical domain was used as weight for the
corresponding direction (Fig.~\ref{fig:DirectionWeights2D3D}).

@@

% Example of reconstruction of a discrete disk
\begin{figure}[!htb]
\begin{center}
\includegraphics[width=12cm]{images/discreteDisks2}
\end{center}
\caption{Discretization of two disks with same radius and different positions. 
A grid cell belong tho the reconstructed shape if its center is inside the original shape.
The reconstructed shapes have different size and shape.}
\label{fig:DiskDiscretization}
\end{figure}

@@

For each test shape, measurements were made on
several discretisation of the shape, with various orientations and various origins.
The center of each shape was chosen at random within the center pixel or voxel of the grid.

@@

% \subsection{Timing evaluation}
% ???

@@

Figure \ref{fig:MeasureSquareOriented} shows measures obtained on discretized squares (side 30 pixels)
with various orientations. All methods oscillate around the expected value. 
Using Crofton method with only 2 directions can produce greater errors on the measure than with 4 
directions. However, in both cases, the average over the orientations of the mean values is very close 
to the actual perimeter.

% Example of reconstruction of a discrete squares with various orientations
\begin{figure}[!htb]
\begin{center}
\includegraphics[width=8cm]{images/perimRotatedSquares}
\includegraphics[width=8cm]{images/errorRotatedSquares}
\end{center}
\caption{Variations of perimeter measure of a digitized square depending on the orientation. 
Left: perimeter measures. Right: relative errors (in percent).}
\label{fig:MeasureSquareOriented}
\end{figure}

% TODO mesure pour des formes 3D
% able

\subsection{Surface area of 3D shapes}

Comarison of surface area measured on several discrete reconstructed shapes is given in
Table \ref{tab:CompareSurfaceArea}.
As for the planar case, the measure is closer to the actual value when using more
directions. The error is around 2 percent in average for 3 directions, and less than
1 percent for 13 directions.

When using isosurface reconstruction, the surface area is systematically over estimated.
The difference is around 8 percent in average.

\begin{table}[!htb]
\begin{center}\begin{tabular}{ccccccc}
shape	& $(\varphi,\theta)$ & $S$ 	& $S_{crofton}^3$ & $S_{crofton}^{13}$ & $S_{isosurface}$ \tabularnewline \hline 
ball 		& $n.a.$  		& 	$11309.8$	& $11312.0$ 	& $11306.6$ 	& $12253.9$ 	\tabularnewline 
prolate	& $( 0,  0)$  	& 	$3082.9$ 	& $2938.7$ 	& $3084.6$ 	& $3344.4$ 	\tabularnewline
- 			& $(45,  0)$  	& 	$-$ 		& $3137.3$ 	& $3086.3$ 	& $3340.6$ 	\tabularnewline
- 			& $(45, 45)$  	& 	$-$ 		& $3150.6$ 	& $3083.3$ 	& $3337.8$ 	\tabularnewline
oblate 	& $( 0,  0)$  	& 	$6856.8$ 	& $6290.7$ 	& $6807.6$ 	& $7387.4$ 	\tabularnewline
- 			& $(45,  0)$  	& 	$-$ 		& $6872.0$ 	& $6789.0$ 	& $7346.2$ 	\tabularnewline
- 			& $(45, 45)$  	& 	$-$ 		& $7154.7$ 	& $6808.5$ 	& $7366.1$ 	\tabularnewline
torus 		& $( 0,  0)$  	& 	$11843.5$	& $11417.3$ 	& $11792.9$ 	& $12785.4$ 	\tabularnewline
-			& $(45,  0)$  	& 	$-$    	& $11809.3$ 	& $11766.8$ 	& $12844.4$ 	\tabularnewline
- 			& $(45, 45)$ 	& 	$-$ 	 	& $12086.0$ 	& $11822.4$ 	& $12798.4$ 	\tabularnewline
\end{tabular}\end{center}
\caption{ \label{tab:CompareSurfaceArea}
Differences between actual surface area and its measures with different methods, 
on shapes with various orientations.
The orientation is given by the direction of the shape rotation axis, defined by 
the azimut $\varphi$ (between 0 and 360 degrees) and the colatitude $\theta$ (between 0 and 180 degrees).}
\end{table}

% \section{Timing}
% [c'est rapide]
